---
title: "Code Book"
author: "Rahulg13"
date: "13/12/2019"
output: pdf_document
---

## **VARIABLES**
Following are the variables used in the script run_analysis.R for the purpose of creating tidy data set for the Samsung Phone sensor data.

```{r pressure, echo=FALSE}
#Creating variable lists
```
1. vardata : reads variable names from feature.txt 
2. variables : contains separated variable names from vardata
3. act_label : reads activity labels from activity_labels.txt
4. actlabels : contains separated variable names from act_label
5. xtest1 : reads test data from X_test.txt file
6. subjecttest : subject data for test entries 
7. ytest : activity data for test entries
8. xtraining : reads training data from X_training.txt file
9. subjecttraining : subject data for training entries 
10. ytrain :activity data for training entires
11. testdata : collated test data with activity, subject and observations
12. traindata : collated training data with activity, subject and observations
13. fulldata : combined test and training data
14. mean_index : the indices of columns where mean variables exist
15. mean_data : the mean values for measurements
16. std_index : the indices of columns where standard deviation variables exist
17. std_index : the standard deviation values for measurements
18. fulldata2 : contains combined data of mean and standard deviation
19. ans : final tidy data set 

## Variable in the tidy.txt are - 

```{r}
ans <- read.table("tidydata.txt", header =  TRUE)
names(ans)
```